Every Author as First Author

### 2023-04-03 paper.tex
Cite round-robin documents
hyperref option needed for arXiv

%
% the following standard packages may be helpful, but are not required
%
%\usepackage{courier}            % standard fixed width font
\usepackage{graphicx}
\usepackage[scaled]{helvet} % see www.ctan.org/get/macros/latex/required/psnfss/psnfss2e.pdf
\usepackage[hyphens,spaces,obeyspaces]{url}
\usepackage{enumitem}      % adjust spacing in enums
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   % hyperlinks, including DOIs and URLs in bibliography
% known bug: http://tex.stackexchange.com/questions/1522/pdfendlink-ended-up-in-different-nesting-level-than-pdfstartlink
\newcommand{\doi}[1]{doi:~\href{http://dx.doi.org/#1}{\Hurl{#1}}}   % print a hyperlinked DOI

@@

A final issue is that overlapping name stacks are not easy to read.
It may be possible to write names in a way that has no first name
but still makes all names clearly readable.
For example, a circle has no beginning or end, so arranging the names
in a circular pattern avoids arranging any author ``first''.
Figure~\ref{fig:circles} shows some initial experiments in this direction.
It remains unsolved how to fit such circular arrangements
in with the rest of a text document, which feels inherently sequential.
Circular arrangements also seem difficult to apply to small numbers of
authors such as $2$.

>>>>

%
% the following standard packages may be helpful, but are not required
%
%\usepackage{courier}            % standard fixed width font
\usepackage{graphicx}
\usepackage[scaled]{helvet} % see www.ctan.org/get/macros/latex/required/psnfss/psnfss2e.pdf
\usepackage[hyphens,spaces,obeyspaces]{url}
\usepackage{enumitem}      % adjust spacing in enums
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false,unicode]{hyperref}   % hyperlinks, including DOIs and URLs in bibliography
% known bug: http://tex.stackexchange.com/questions/1522/pdfendlink-ended-up-in-different-nesting-level-than-pdfstartlink
\newcommand{\doi}[1]{doi:~\href{http://dx.doi.org/#1}{\Hurl{#1}}}   % print a hyperlinked DOI

@@

A final issue is that overlapping name stacks are not easy to read.
It may be possible to write names in a way that has no first name
but still makes all names clearly readable.
For example, a circle has no beginning or end, so arranging the names
in a circular pattern avoids arranging any author ``first''.
Figure~\ref{fig:circles} shows some initial experiments in this direction.
Related, traditional \emph{round-robin} documents \cite{round-robin}
are signed by authors in a circle to prevent identification of a ringleader
(such as mutineer sailors).
It remains unsolved how to fit such circular arrangements
in with the rest of a text document, which feels inherently sequential.
Circular arrangements also seem difficult to apply to small numbers of
authors such as $2$.
